Secure Composition \\ of Robust and Optimising Compilers

### 2024-05-10 csf2/main.tex
add csf2
figure fitting

% Fixing: Too many math alphabets used in version normal.
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[dvipsnames]{llncs}

@@

\usepackage[colorinlistoftodos]{todonotes}
\usepackage[inference]{semantic}
\usepackage{lineno}
\usepackage{fontawesome5}
\usepackage{listofitems}
\usepackage{breakcites}
\usepackage{glossaries}
%\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{marvosym}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{nameref}
%\usepackage{amsthm}
\usepackage{xspace}
\usepackage{xfrac}
\usepackage{tikz}
\usepackage{soul}
\usepackage{bm}

%\renewcommand\UrlFont{\color{blue}\rmfamily}
\newcommand{\url}[1]{\lstinline{#1}}

@@

@@

\newtheorem{exampleenv}{Example}[section]
%\newtheorem{lemma}{Lemma}[section]
%\newtheorem{theorem}{Theorem}[section]
%\newtheorem{corollary}{Corollary}[section]
%\newtheorem{definition}{Definition}[section]

@@

@@

\institute{}
% CISPA Helmholtz Center for Information Security and Saarland University
% \and
% CISPA Helmholtz Center for Information Security
% \and
% Trento University
% }

% \email{matthis.kruse@cispa.de \and director@cispa.de \and marco.patrignani@unitn.it}

@@

\begin{center}\small\it
	{This paper uses syntax highlighting accessible to both colourblind and black \& white readers.
	% ~\cite{patrignani2020use}.
% 	% Specifically, it makes use of a $\src{blue}$, $\src{sans\text{-}serif}$ font for a $\src{source}$,
% 	% a $\trg{red}$, $\trg{bold}$ font for an $\trg{intermediate}$,
% 	% and a $\obj{green}$, $\obj{teletype}$ font for a $\obj{target}$ language.
	}
\end{center}
\keywords{memory-safety, secure compilation, formal methods}
\end{abstract}

@@

This section introduces a trace model and uses it to define the key properties of interest for this paper: \gls*{tms}, \gls*{sms}, \gls*{ms}, and \gls*{scct} (\Cref{subsec:propdefs}).
These properties are of practical importance (as mentioned in \Cref{sec:introduction}) and also of interest in the case study (\Cref{sec:casestud:defs,sec:casestud:rtp}) this paper presents later. 
Lastly, for each of the key properties, this section introduces corresponding monitors (\Cref{subsec:monitors}) that check them.

@@

  \noindent
  $
  \smssafe:=\left\{\trace \left|\begin{array}{rcl}
                                  \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}, \text{ then }m<n
                                \end{array}\right.\right\}
                                $
  % \end{nscenter}
\end{definition}

@@

  \noindent$
  \scctsafe:=\left\{\trace \left|\begin{array}{rcl}
                                   \trace=\hole{\cdot} & \text{ or } & \trace=\event[_{b}];\sandboxtag;\unlock\cdot\trace['] \wedge \trace[']\in\scctsafe
                                 \end{array}\right.\right\}
  $
% \end{nscenter}
\end{definition}

@@

%\section{Monitors and Trace Agreements\pages{1.5}}\label{subsec:monitors}
\subsection{Monitors\pages{1.5}}\label{subsec:monitors}

Monitors enforce safety properties by accepting or rejecting traces, i.e., if they reject a trace, the trace does not satisfy the property they check.
Since reasoning on monitors is easier than on just traces, this section presents a monitor for each of the previously shown safety properties (\Cref{subsec:propdefs}).
%\MPpost{
%	this is fine, but it'd be nice to provide more insights on why it's easier
%}
To lessen the burden when proving that a monitor accepts the trace of a program execution, each monitor uses a custom trace model that contains only the relevant information related to the property the monitor checks.
To go from specification traces $\trace$ to monitor-level traces $\abstrace$, each property $\pi$ has an associated event agreement relation $\traceagree[]{\pi}{\event}{\absevent}$.
Lifting the event agreement to traces works as expected, i.e., the empty traces are related, both are allowed to stutter with the empty event, and otherwise the events $\event$ and $\absevent$ must fulfill $\traceagree[]{\pi}{\event}{\absevent}$.
The trace agreement is the same for all properties $\pi$. 
With agreements, this section defines monitor satisfaction for traces and then it proves that monitor satisfaction implies property satisfaction.
To this end, monitor satisfaction is defined as follows.
\bul{A specification trace $\trace$ monitor-satisfies property $\pi$} iff there exists a (final) monitor state $\monitor$ and an abstract trace $\abstrace$ such that the \iul{specification trace $\trace$ agrees with abstract trace $\abstrace$} and \oul{the initial monitor\footnote{In this paper, for all monitors, the initial monitor state is denoted as $\emptyset$.} can step to the (final) monitor state $\monitor$ with abstract trace $\abstrace$}.

\begin{definition}[Monitor Satisfaction]\label{def:monsat}
  \bul{$\monsafe{\trace}{\pi}$} $\isdef$ $\exists \abstrace\ \monitor$, \iul{$\traceagree{\pi}{\trace}{\abstrace}$} and \oul{$\monitorcheck{\emptyset}{\monitor}{\abstrace}$}.
\end{definition}

\subsubsection{Monitor for \glsfirst*{tms}}\label{subsubsec:tms}
\begin{gather*}
  \begin{aligned}
    \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{A}:L\times\sandboxtag,\text{F}:L\times\sandboxtag\right\} 
    \\%
    % \emptyset:=&\ \left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}
    % \\
    \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc\ \sandboxtag \mid \absev{Dealloc\ }\loc\ \sandboxtag 
    % \\
                                            % & 
                                            \mid \absev{Use\ }\loc\ \sandboxtag \mid \absterm\\
  \end{aligned}
\end{gather*}
For \gls*{tms}, the state of the monitor is a record with two sets keeping track of allocated and deallocated locations, and the initial state $\emptyset$ is defined as $\left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}$.
% 
Monitor events include {\em allocation}, {\em deallocation}, and {\em use} of a location $\loc$ as well as abnormal program termination.

\begin{center}\small
  \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
  %
% \typerule{tms-uninteresting}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
% }{tms-uninteresting}
% %
% \typerule{tms-abort}{
% }{
%   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
% }{tms-abort}
  % 
  \typerule{tms-use}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    % \\
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
  }{tms-use}
  %
  \typerule{tms-alloc}{
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{A} &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    % \\
    &
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\cup\left\{(\loc;\sandboxtag)\right\},\text{F}: \tmsmonitor.\text{F}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc}
  %
  \typerule{tms-dealloc}{
    (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
    &
    (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
    \\
    \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\setminus\left\{(\loc;\sandboxtag)\right\} \text{F}: \tmsmonitor.\text{F}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
  }{tms-dealloc}
  %
\end{center}
% 
\Cref{tr:tms-use} simply requires that a location is (i) allocated and (ii) not freed.
\Cref{tr:tms-alloc,tr:tms-dealloc} both require a location to not be freed already and extend the monitor state accordingly.
This restriction effectively disallows reallocation to reassign the same location to an object.
However, the definition can easily be adapted by, e.g., attaching a natural number serving as a counter.
Contrary to other monitors in this paper, the multi-step relation of the \gls*{tms} monitor is non-standard:
\begin{center}
  \judgbox{\monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}}{,,Monitor $\tmsmonitor$ multi-steps to $\tmsmonitor[']$ given trace $\abstrace$.''}$\;$\\
  %
  \typerule{tms-refl}{
    \tmsmonitor.\text{allocated}=\emptyset
  }{
    \monitorcheck{\tmsmonitor}{\tmsmonitor}{\hole{\cdot}}
  }{tms-refl}
  %
  \typerule{tms-ign-trans}{
    \monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{\emptyevent}\cdot\abstrace}
  }{tms-ign-trans}
  %
  \typerule{tms-trans}{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent} &
    \monitorcheck{\tmsmonitor[']}{\tmsmonitor['']}{\abstrace}
  }{
    \monitorcheck[]{\tmsmonitor}{\tmsmonitor['']}{\absevent\cdot\abstrace}
  }{tms-trans}
\end{center}
\Cref{tr:tms-ign-trans,tr:tms-trans} are the same for all monitors, but \Cref{tr:tms-refl} has, in this case, an additional premise that all locations should be deallocated.
This rejects the behavior of programs that forget to free memory.

\begin{center}\small
  \judgbox{\tmstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ w.r.t. \gls*{tms}.''}$\;$\\
  %
  \typerule{tms-alloc-authentic}{
  }{
    \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc\ \sandboxtag}
  }{tms-alloc-authentic}
  %
% \typerule{tms-dealloc-authentic}{
% }{
%   \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
% }{tms-dealloc-authentic}
  %
% \typerule{tms-use-authentic}{
% }{
%   \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
% }{tms-use-authentic}
  %
  \typerule{tms-branch-authentic}{
  }{
    \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
  }{tms-branch-authentic}
  %
% \typerule{tms-binop-authentic}{
% }{
%   \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
% }{tms-binop-authentic}
% %
% \typerule{tms-empty-authentic}{
% }{
%   \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
% }{tms-empty-authentic}
% %
  % \typerule{tms-abort-authentic}{
  % }{
  %   \tmstraceagree[]{\lightning}{\absterm}
  % }{tms-abort-authentic}
\end{center}

The trace agreement maps actions to their respective (e.g., \Cref{tr:tms-alloc-authentic}), so we elide most cases.
% 
Since branches are not relevant for \gls*{tms}, they are mapped to $\absev{\emptyevent}$ (\Cref{tr:tms-branch-authentic}).
% \MP{
% 	we should say something .. ?
% }

\begin{lemma}[Monitor Satisfaction is $\tmssafe$]\label{lem:mon:tmssafe}
  $\;\;$ If $\montmssafe{\trace}$, then $\trace\in\tmssafe$. %\Coqed
\end{lemma}

\begin{exampleenv}[A program not satisfying \gls*{tms}]\label{ex:strncpy:cpp11}
  Consider the following \texttt{C++11} library that calls \texttt{strncpy} (\Cref{ex:strncpy}) and prints the result to the standard output stream.

  \begin{lstlisting}[language=c++,basicstyle=\small\ttfamily,mathescape,commentstyle=\color{gray}]
int hello() {
  char* greet = new char[12] { "Hello ESOP!" };
  char* to = new char[12];
  strncpy(11, to, greetings);
  delete to;
  printf("%cSOP\n", to[6]);
}
  \end{lstlisting}
    % // greet address ${\color{gray}\loc_{x}}$
  % // to address ${\color{gray}\loc_{y}}$
% 
  Up to the body of \texttt{printf}, the program execution yields the specification trace: 
  	% $\ev{Alloc}\ \loc[_{x}]\ 12;\comp;\unlock\cdot\ev{Alloc}\ \loc[_{y}]\ 12;\comp;\unlock\cdot\ev{Use}\ \loc_{x}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{x}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{y}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{x}\ 1;\comp;\unlock\cdot\ldots\cdot\ev{Use}\ \loc_{x}\ 12;\comp;\unlock\cdot\ev{Dealloc}\ \loc[_{y}];\comp;\unlock\cdot\ev{Use}\ \loc_{y}\ 6;\comp;\unlock$

  	\vspace{-1em}
  	{\small
  	\begin{align*}
  		&
  		\ev{Alloc}\ \loc[_{x}]\ 12;\comp;\unlock
  		\cdot
  		\ev{Alloc}\ \loc[_{y}]\ 12;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{x}\ 0;\comp;\unlock
  		\\
  		&
  		\cdot
  		\ev{Use}\ \loc_{x}\ 0;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{y}\ 0;\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{x}\ 1;\comp;\unlock
  		\cdot
  		\ldots
  		\\
  		&
  		\cdot
  		\ev{Use}\ \loc_{x}\ 12;\comp;\unlock
  		\cdot
  		\ev{Dealloc}\ \loc[_{y}];\comp;\unlock
  		\cdot
  		\ev{Use}\ \loc_{y}\ 6;\comp;\unlock
  	\end{align*}
  	}
Relating this trace to abstract monitor events yields trace:

  \vspace{-1em}
  {\small
  \begin{align*}
   	% \abstrace=
   	&
   	\absev{Alloc}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Alloc}\ \loc[_{y}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	% \\
   	% &
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{y}]\ \comp
   	\cdot
   	\ldots
   	\\
   	&
   	\cdot
   	\absev{Use}\ \loc[_{x}]\ \comp
   	\cdot
   	\absev{Dealloc}\ \loc[_{y}]\ \comp
   	\cdot
   	\absev{Use}\ \loc[_{y}]\ \comp
   \end{align*} 
  	}
  Remembering the definition of \texttt{strncpy} (\Cref{ex:strncpy}), observe that it does not deallocate its arguments.
  Even though the trace contains an out-of-bounds access right before returning from \texttt{strncpy}, this is no concern for \gls*{tms}, since location $\loc[_{x}]$ is still allocated.
  Having returned from \texttt{strncpy}, the \texttt{greet} function continues and deallocates $\loc[_{y}]$ whose subsequent use in \texttt{printf} is a use-after-free bug.

  The fix would be to \lstinline[language=c++,basicstyle=\small\ttfamily]|delete greetings| instead of \texttt{to} and add a \lstinline[language=c++,basicstyle=\small\ttfamily]|delete to| after the \texttt{printf} call, which leads to trace:

>>>>

% Fixing: Too many math alphabets used in version normal
\newcommand\hmmax{0}
\newcommand\bmmax{0}
\documentclass[dvipsnames,conference]{IEEEtran}

@@

\usepackage[colorinlistoftodos]{todonotes}
\usepackage[inference]{semantic}
\usepackage[switch]{lineno}
\usepackage{fontawesome5}
\usepackage{listofitems}
\usepackage{breakcites}
\usepackage{glossaries}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{stmaryrd}
\usepackage{marvosym}
\usepackage{listings}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{nameref}
\usepackage{amsthm}
\usepackage{xspace}
\usepackage{xfrac}
\usepackage{tikz}
\usepackage{soul}
\usepackage{bm}

%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\newcommand{\url}[1]{\lstinline{#1}}

@@

% allow page breaks inside multiline alignment displays
\allowdisplaybreaks

@@

\theoremstyle{definition}
\newtheorem{exampleenv}{Example}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{definition}{Definition}[section]

@@

\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
\makeatletter
\newcommand{\linebreakand}{%
  \end{@IEEEauthorhalign}
  \hfill\mbox{}\par
  \mbox{}\hfill\begin{@IEEEauthorhalign}
}
\makeatother

@@

@@

\begin{center}\small\it
	{This paper uses syntax highlighting accessible to both colourblind and black \& white readers.
	% ~\cite{patrignani2020use}.
% 	% Specifically, it makes use of a $\src{blue}$, $\src{sans\text{-}serif}$ font for a $\src{source}$,
% 	% a $\trg{red}$, $\trg{bold}$ font for an $\trg{intermediate}$,
% 	% and a $\obj{green}$, $\obj{teletype}$ font for a $\obj{target}$ language.
	}
\end{center}
\end{abstract}

\begin{IEEEkeywords}
  memory-safety, cryptographic constant-time, secure compilation, robustness
\end{IEEEkeywords}

@@

This section introduces a trace model and uses it to define the key properties of interest for this paper: \gls*{tms}, \gls*{sms}, \gls*{ms}, and \gls*{scct} (\Cref{subsec:propdefs}).
These properties are of practical importance (as mentioned in \Cref{sec:introduction}) and also of interest in the case study (\Cref{sec:casestud:defs,sec:casestud:rtp}) this paper presents later.

@@

  \noindent
  $$
  \smssafe:=\left\{\trace \left|\begin{array}{rcl}
                                  \text{If }\ev{Alloc\ \loc\ n;\sandboxtag;\securitytag}\le_{\trace}\ev{Use\ \loc\ m;\sandboxtag;\securitytag'}, \text{ then }m<n
                                \end{array}\right.\right\}
                                $$
  % \end{nscenter}
\end{definition}

@@

  \noindent$$
  \scctsafe:=\left\{\trace \left|\begin{array}{rcl}
                                   \trace=\hole{\cdot} & \text{ or } & \trace=\event[_{b}];\sandboxtag;\unlock\cdot\trace['] \wedge \trace[']\in\scctsafe
                                 \end{array}\right.\right\}
  $$
% \end{nscenter}
\end{definition}

@@

%\section{Monitors and Trace Agreements\pages{1.5}}\label{subsec:monitors}
% \subsection{Monitors\pages{1.5}}\label{subsec:monitors}

% Monitors enforce safety properties by accepting or rejecting traces, i.e., if they reject a trace, the trace does not satisfy the property they check.
% Since reasoning on monitors is easier than on just traces, this section presents a monitor for each of the previously shown safety properties (\Cref{subsec:propdefs}).
% %\MPpost{
% %	this is fine, but it'd be nice to provide more insights on why it's easier
% %}
% To lessen the burden when proving that a monitor accepts the trace of a program execution, each monitor uses a custom trace model that contains only the relevant information related to the property the monitor checks.
% To go from specification traces $\trace$ to monitor-level traces $\abstrace$, each property $\pi$ has an associated event agreement relation $\traceagree[]{\pi}{\event}{\absevent}$.
% Lifting the event agreement to traces works as expected, i.e., the empty traces are related, both are allowed to stutter with the empty event, and otherwise the events $\event$ and $\absevent$ must fulfill $\traceagree[]{\pi}{\event}{\absevent}$.
% The trace agreement is the same for all properties $\pi$. 
% With agreements, this section defines monitor satisfaction for traces and then it proves that monitor satisfaction implies property satisfaction.
% To this end, monitor satisfaction is defined as follows.
% \bul{A specification trace $\trace$ monitor-satisfies property $\pi$} iff there exists a (final) monitor state $\monitor$ and an abstract trace $\abstrace$ such that the \iul{specification trace $\trace$ agrees with abstract trace $\abstrace$} and \oul{the initial monitor\footnote{In this paper, for all monitors, the initial monitor state is denoted as $\emptyset$.} can step to the (final) monitor state $\monitor$ with abstract trace $\abstrace$}.

% \begin{definition}[Monitor Satisfaction]\label{def:monsat}
%   \bul{$\monsafe{\trace}{\pi}$} $\isdef$ $\exists \abstrace\ \monitor$, \iul{$\traceagree{\pi}{\trace}{\abstrace}$} and \oul{$\monitorcheck{\emptyset}{\monitor}{\abstrace}$}.
% \end{definition}

% \subsubsection{Monitor for \glsfirst*{tms}}\label{subsubsec:tms}
% \begin{gather*}
%   \begin{aligned}
%     \mi{(Abstract\ Store)}~\tmsmonitor\bnfdef&\ \left\{\text{A}:L\times\sandboxtag,\text{F}:L\times\sandboxtag\right\} 
%     \\%
%     % \emptyset:=&\ \left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}
%     % \\
%     \mi{(Abstract\ Events)}~\absevent\bnfdef&\ \absev{\emptyevent} \mid \absev{Alloc\ }\loc\ \sandboxtag \mid \absev{Dealloc\ }\loc\ \sandboxtag 
%     % \\
%                                             % & 
%                                             \mid \absev{Use\ }\loc\ \sandboxtag \mid \absterm\\
%   \end{aligned}
% \end{gather*}
% For \gls*{tms}, the state of the monitor is a record with two sets keeping track of allocated and deallocated locations, and the initial state $\emptyset$ is defined as $\left\{\text{A}:\emptyset,\text{F}:\emptyset\right\}$.
% % 
% Monitor events include {\em allocation}, {\em deallocation}, and {\em use} of a location $\loc$ as well as abnormal program termination.

% \begin{center}\small
%   \judgbox{\monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent}}{,,Monitor $\tmsmonitor$ steps to $\tmsmonitor[']$ given event $\absevent$.''}$\;$\\
%   %
% % \typerule{tms-uninteresting}{
% % }{
% %   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{\emptyevent}}
% % }{tms-uninteresting}
% % %
% % \typerule{tms-abort}{
% % }{
% %   \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absterm}
% % }{tms-abort}
%   % 
%   \typerule{tms-use}{
%     (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
%     &
%     % \\
%     (\loc;\sandboxtag)\notin\tmsmonitor.\text{F}
%   }{
%     \monitorcheck[]{\tmsmonitor}{\tmsmonitor}{\absev{Use\ }\loc\ \sandboxtag}
%   }{tms-use}
%   %
%   \typerule{tms-alloc}{
%     (\loc;\sandboxtag)\notin\tmsmonitor.\text{A} &
%     (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
%     % \\
%     &
%     \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\cup\left\{(\loc;\sandboxtag)\right\},\text{F}: \tmsmonitor.\text{F}\right\}
%   }{
%     \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Alloc\ }\loc\ \sandboxtag}
%   }{tms-alloc}
%   %
%   \typerule{tms-dealloc}{
%     (\loc;\sandboxtag)\in\tmsmonitor.\text{A} 
%     &
%     (\loc;\sandboxtag)\notin\tmsmonitor.\text{F} 
%     \\
%     \tmsmonitor[']=\left\{\text{A}: \tmsmonitor.\text{A}\setminus\left\{(\loc;\sandboxtag)\right\} \text{F}: \tmsmonitor.\text{F}\cup\left\{(\loc;\sandboxtag)\right\}\right\}
%   }{
%     \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{Dealloc\ }\loc\ \sandboxtag}
%   }{tms-dealloc}
%   %
% \end{center}
% % 
% \Cref{tr:tms-use} simply requires that a location is (i) allocated and (ii) not freed.
% \Cref{tr:tms-alloc,tr:tms-dealloc} both require a location to not be freed already and extend the monitor state accordingly.
% This restriction effectively disallows reallocation to reassign the same location to an object.
% However, the definition can easily be adapted by, e.g., attaching a natural number serving as a counter.
% Contrary to other monitors in this paper, the multi-step relation of the \gls*{tms} monitor is non-standard:
% \begin{center}
%   \judgbox{\monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}}{,,Monitor $\tmsmonitor$ multi-steps to $\tmsmonitor[']$ given trace $\abstrace$.''}$\;$\\
%   %
%   \typerule{tms-refl}{
%     \tmsmonitor.\text{allocated}=\emptyset
%   }{
%     \monitorcheck{\tmsmonitor}{\tmsmonitor}{\hole{\cdot}}
%   }{tms-refl}
%   %
%   \typerule{tms-ign-trans}{
%     \monitorcheck{\tmsmonitor}{\tmsmonitor[']}{\abstrace}
%   }{
%     \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absev{\emptyevent}\cdot\abstrace}
%   }{tms-ign-trans}
%   %
%   \typerule{tms-trans}{
%     \monitorcheck[]{\tmsmonitor}{\tmsmonitor[']}{\absevent} &
%     \monitorcheck{\tmsmonitor[']}{\tmsmonitor['']}{\abstrace}
%   }{
%     \monitorcheck[]{\tmsmonitor}{\tmsmonitor['']}{\absevent\cdot\abstrace}
%   }{tms-trans}
% \end{center}
% \Cref{tr:tms-ign-trans,tr:tms-trans} are the same for all monitors, but \Cref{tr:tms-refl} has, in this case, an additional premise that all locations should be deallocated.
% This rejects the behavior of programs that forget to free memory.

% \begin{center}\small
%   \judgbox{\tmstraceagree[]{\event}{\absevent}}{,,Abstract event $\absevent$ is equivalent to $\event$ w.r.t. \gls*{tms}.''}$\;$\\
%   %
%   \typerule{tms-alloc-authentic}{
%   }{
%     \tmstraceagree[]{\ev{Alloc}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Alloc\ }\loc\ \sandboxtag}
%   }{tms-alloc-authentic}
%   %
% % \typerule{tms-dealloc-authentic}{
% % }{
% %   \tmstraceagree[]{\ev{Dealloc}\ \loc;\sandboxtag;\securitytag}{\absev{Dealloc\ }\loc}
% % }{tms-dealloc-authentic}
%   %
% % \typerule{tms-use-authentic}{
% % }{
% %   \tmstraceagree[]{\ev{Use}\ \loc\ n;\sandboxtag;\securitytag}{\absev{Use\ }\loc}
% % }{tms-use-authentic}
%   %
%   \typerule{tms-branch-authentic}{
%   }{
%     \tmstraceagree[]{\ev{Branch\ }n}{\absev{\emptyevent}}
%   }{tms-branch-authentic}
%   %
% % \typerule{tms-binop-authentic}{
% % }{
% %   \tmstraceagree[]{\ev{Binop\ }n}{\absev{\emptyevent}}
% % }{tms-binop-authentic}
% % %
% % \typerule{tms-empty-authentic}{
% % }{
% %   \tmstraceagree[]{\emptyevent}{\absev{\emptyevent}}
% % }{tms-empty-authentic}
% % %
%   % \typerule{tms-abort-authentic}{
%   % }{
%   %   \tmstraceagree[]{\lightning}{\absterm}
%   % }{tms-abort-authentic}
% \end{center}

% The trace agreement maps actions to their respective (e.g., \Cref{tr:tms-alloc-authentic}), so we elide most cases.
% % 
% Since branches are not relevant for \gls*{tms}, they are mapped to $\absev{\emptyevent}$ (\Cref{tr:tms-branch-authentic}).
% % \MP{
% % 	we should say something .. ?
% % }

% \begin{lemma}[Monitor Satisfaction is $\tmssafe$]\label{lem:mon:tmssafe}
%   $\;\;$ If $\montmssafe{\trace}$, then $\trace\in\tmssafe$. %\Coqed
% \end{lemma}

% \begin{exampleenv}[A program not satisfying \gls*{tms}]\label{ex:strncpy:cpp11}
%   Consider the following \texttt{C++11} library that calls \texttt{strncpy} (\Cref{ex:strncpy}) and prints the result to the standard output stream.

%   \begin{lstlisting}[language=c++,basicstyle=\small\ttfamily,mathescape,commentstyle=\color{gray}]
% int hello() {
%   char* greet = new char[12] { "Hello ESOP!" };
%   char* to = new char[12];
%   strncpy(11, to, greetings);
%   delete to;
%   printf("%cSOP\n", to[6]);
% }
%   \end{lstlisting}
%     % // greet address ${\color{gray}\loc_{x}}$
%   % // to address ${\color{gray}\loc_{y}}$
% % 
%   Up to the body of \texttt{printf}, the program execution yields the specification trace: 
%     % $\ev{Alloc}\ \loc[_{x}]\ 12;\comp;\unlock\cdot\ev{Alloc}\ \loc[_{y}]\ 12;\comp;\unlock\cdot\ev{Use}\ \loc_{x}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{x}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{y}\ 0;\comp;\unlock\cdot\ev{Use}\ \loc_{x}\ 1;\comp;\unlock\cdot\ldots\cdot\ev{Use}\ \loc_{x}\ 12;\comp;\unlock\cdot\ev{Dealloc}\ \loc[_{y}];\comp;\unlock\cdot\ev{Use}\ \loc_{y}\ 6;\comp;\unlock$

%     \vspace{-1em}
%     {\small
%     \begin{align*}
%       &
%       \ev{Alloc}\ \loc[_{x}]\ 12;\comp;\unlock
%       \cdot
%       \ev{Alloc}\ \loc[_{y}]\ 12;\comp;\unlock
%       \cdot
%       \ev{Use}\ \loc_{x}\ 0;\comp;\unlock
%       \\
%       &
%       \cdot
%       \ev{Use}\ \loc_{x}\ 0;\comp;\unlock
%       \cdot
%       \ev{Use}\ \loc_{y}\ 0;\comp;\unlock
%       \cdot
%       \ev{Use}\ \loc_{x}\ 1;\comp;\unlock
%       \cdot
%       \ldots
%       \\
%       &
%       \cdot
%       \ev{Use}\ \loc_{x}\ 12;\comp;\unlock
%       \cdot
%       \ev{Dealloc}\ \loc[_{y}];\comp;\unlock
%       \cdot
%       \ev{Use}\ \loc_{y}\ 6;\comp;\unlock
%     \end{align*}
%     }
% Relating this trace to abstract monitor events yields trace:
%   
%   \vspace{-1em}
%   {\small
%   \begin{align*}
%     % \abstrace=
%     &
%     \absev{Alloc}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Alloc}\ \loc[_{y}]\ \comp
%     \cdot
%     \absev{Use}\ \loc[_{x}]\ \comp
%     % \\
%     % &
%     \cdot
%     \absev{Use}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Use}\ \loc[_{y}]\ \comp
%     \cdot
%     \ldots
%     \\
%     &
%     \cdot
%     \absev{Use}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Dealloc}\ \loc[_{y}]\ \comp
%     \cdot
%     \absev{Use}\ \loc[_{y}]\ \comp
%    \end{align*} 
%     }
%   Remembering the definition of \texttt{strncpy} (\Cref{ex:strncpy}), observe that it does not deallocate its arguments.
%   Even though the trace contains an out-of-bounds access right before returning from \texttt{strncpy}, this is no concern for \gls*{tms}, since location $\loc[_{x}]$ is still allocated.
%   Having returned from \texttt{strncpy}, the \texttt{greet} function continues and deallocates $\loc[_{y}]$ whose subsequent use in \texttt{printf} is a use-after-free bug.

%   The fix would be to \lstinline[language=c++,basicstyle=\small\ttfamily]|delete greetings| instead of \texttt{to} and add a \lstinline[language=c++,basicstyle=\small\ttfamily]|delete to| after the \texttt{printf} call, which leads to trace: 
%   
% \vspace{-1em}
%   {\small
%   \begin{align*}
%     \abstrace[']=
%     &
%     \absev{Alloc}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Alloc}\ \loc[_{y}]\ \comp
%     \cdot
%     \absev{Use}\ \loc[_{x}]\ \comp
%     % \\
%     % &
%     \cdot
%     \absev{Use}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Use}\ \loc[_{y}]\ \comp
%     \cdot
%     \ldots
%     \cdot
%     \\
%     &
%     \absev{Use}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Dealloc}\ \loc[_{x}]\ \comp
%     \cdot
%     \absev{Use}\ \loc[_{y}]\ \comp	
%   \end{align*}
%   }
%   It follows that $\montmssafe{\abstrace[']}$ and from \Thmref{lem:mon:tmssafe}, it follows that the program satisfies \Thmref{def:trace:tmsdef}, even though the program still violates \gls*{sms}.
% \end{exampleenv}

% % \MPpost{
% % 	i think the trace description of traces is more uindertandable,
% % 	teh monitor one is easier to work with
% % 	this is the justification for having both that we'll have to make in the future
% % }
